---
title: "Stat Final"
author: "Sangseok Lee"
date: "11/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lattice)
library(mice)
library(VIM)
library(tidyverse)
library(dplyr)
library(arm)
library(pROC)
library(e1071)
library(caret)
library(lme4)
library(rstan)

```

## Intro

In today’s busy world, finding and dating a romantic partner seems more time consuming than ever. As a result, many people have turned to speed dating as a solution that allows one to meet a large number of potential partners during a short amount of time. In this report, I want to explore what speed dating takes to become successful in getting approvals from a potential partner. In addition, since matching is more important than just decision, 
I am going to explore what factors really affect their matching. 

## Data 
1. Decision model by male and female: I would like to know which variables are the main factors to make people choose. 
2. Matching model by male and female : I would like to know which variables are the main factors to make people choose each other.

In order to answer the first question, I use the dataset with 8378 rows and 15 columns and my response variable would be 'dec'variable. In addition, to answer the second question, I only select the people who decide their partner, which brings the dataset with 3375 rows and 23 columns. My response variable for the second model is 'match' variable. 


```{r, include=FALSE}
#read data
dating <-read.csv("/Users/josephlee/myproject/Speed_Dating/0_data/Speed_Dating_Data.csv", sep = ",", header = TRUE)

# first subset for selecting (one way)
dating1<- subset(dating, select = c('iid','wave', 'pid','dec','gender','attr','sinc','intel','fun','amb',
'shar','samerace','age_o','prob','like'))
summary(dating1)
#there are 10 NAs in pid column from wave 5, and they should not be deleted since they give information. I give 118 because only this iid was not evaluated by other partners.


dating_na<-dating1 %>% filter(is.na(pid))
dating1$pid[is.na(dating1$pid)] <- 118

#remove rows when all 6 attributes are NAs : 192 variables 
#dating2 <- subset(dating1, !is.na(dating1$attr) & !is.na(dating1$sinc) & !is.na(dating1$intel) & !is.na(dating1$fun) & !is.na(dating1$amb) & !is.na(dating1$shar))

# remove 104 NAs from age_o since we have no clue 
dating2 <- dating1 %>% filter(!is.na(age_o))
# remove 295 NAs from prob since we have no clue
dating2 <- dating2 %>% filter(!is.na(prob))
# remove 15 NAs from like since we have no clue
dating2 <- dating2 %>% filter(!is.na(like))
summary(dating2)

# remove 5 rows with all NAs
cnt_na <- apply(dating2, 1, function(z) sum(is.na(z)))
dating3 <- dating2[cnt_na < 6,]



#summary(dating2)
#to see all rows with any NAs
#d <- dating1[is.na(dating1$attr) & is.na(dating1$sinc) &  is.na(dating1$fun) & is.na(dating1$amb) & is.na(dating1$shar), ]


#d <- dating2[is.na(dating2$attr) & is.na(dating2$sinc) &  is.na(dating2$fun) & is.na(dating2$amb) & is.na(dating2$shar) , ]

#change factor variable
str(dating3)
dating3$dec <- factor(dating3$dec)
dating3$gender <- factor(dating3$gender)
dating3$samerace <- factor(dating3$samerace)

summary(dating3)



```
## 1-1. First model for the first question
My response variable is 'dec' column and predictors are 11 variables: 'gender','attr','sinc','intel','fun','amb','shar','samerace','age_o','prob','like'. 

# 1) Data Cleaning : missing values
Frist of all, there are 10 NAs in pid(partner ID) column from wave 5, and they can be inferred as 118 because people in wave 5 evaluated everyone except 118 as iid. 
Second, I dropped 414 rows including missing values that we cannot estimate from 'age_0', 'prob', 'like' columns. 5 no evaluation rows on all six variables(attr,sinc,intel,fun,amb,shar) is also removed because they do not give us any information for the decision. Third, we changed dec(decision), gender, samerace columns as facor variables. Still, we have about 1,000 missing values(about 15% of the dataset).

```{r, echo= FALSE}
#md.pattern(dating3)
#filter each columns
#dating_n <- dating2 %>% filter(is.na(attr) &is.na(shar)&is.na(sinc)& is.na(intel)& is.na(fun)& is.na(amb))
#dating_n <- dating2 %>% filter(is.na(attr))
#dating_n <- dating_n %>% filter(!is.na(shar))
#dating_n <- dating_n %>% filter(!is.na(sinc))
#dating_n <- dating_n %>% filter(!is.na(intel))
#dating_n <- dating_n %>% filter(!is.na(fun))
#dating_n <- dating_n %>% filter(!is.na(amb))


aggr(dating3,col=c("lightblue3","darkred"),numbers=TRUE,sortVars=TRUE,labels=names(dating1),cex.axis=.7,gap=3,ylab=c("Proportion missing","Missingness pattern"))

# marginplot(dating3[,c("shar","dec")],col=c("lightblue3","darkred"),cex.numbers=1.2,pch=19)
```


#2) Data  Cleaning : imputed data 
Since some variables such as sinc, intel, amb and shar are relatively hard to estimate with imputed data compared with other variables such as attr and fun, I used two ways for imputation. 
1. Imputation only for attr, fun (removal for NAs in sinc, intel, amb and shar)
2. Imputation for every missing values in all six variables
I am going to compare two models and decide which model is better. From the first way of imputation, I used 'pmm' because imputed values keeps observed values rathers than 'norm' way

In order to avoid multi-collinearity, I made mean-centering for attr, sinc, intel, fun, amb, shar, prob, like. Now I divded this dataset by two : male and female. 

```{r}

# 1. Impute appearance and fun , remove other attributes that are less likely to figure out druing 4 minutes.
dating_n <- dating3 %>% filter(!is.na(sinc))
dating_n <- dating_n %>% filter(!is.na(shar))
dating_n <- dating_n %>% filter(!is.na(intel))
dating_n <- dating_n %>% filter(!is.na(amb))
summary(dating_n)

#we use pmm because imputed values keeps observed values
dating_n_imp <- mice(dating_n,m=1,defaultMethod=c("norm","logreg","polyreg","polr"),print=F)
n1 <- mice::complete(dating_n_imp)

stripplot(dating_n_imp, col=c("grey","darkred"),pch=c(1,20))
densityplot(dating_n_imp)

n1$attr_c = n1$attr - mean(n1$attr)
n1$sinc_c = n1$sinc - mean(n1$sinc)
n1$intel_c = n1$intel - mean(n1$intel)
n1$fun_c = n1$fun - mean(n1$fun)
n1$amb_c = n1$amb - mean(n1$amb)
n1$shar_c = n1$shar - mean(n1$shar)
n1$prob_c = n1$prob - mean(n1$prob)
n1$like_c = n1$like - mean(n1$like)

# we analyze data by sex 
n1_m <- n1[n1$gender=='1',] 
n1_f <- n1[n1$gender=='0',] 

```
# 3 EDA



```{r}
#EDA for first model 

# for different sex
#female prefers to say yes when partner is attractive compared to male?
qplot(x=dec,y=attr,data=n1, facets = ~gender, xlab="decision",ylab="attractive",
      geom="boxplot",fill=dec)
qplot(x=dec,y=sinc,data=n1, facets = ~gender,xlab="decision",ylab="sincere",
      geom="boxplot",fill=dec)
qplot(x=dec,y=intel,data=n1, facets = ~gender,xlab="decision",ylab="intelligent",
      geom="boxplot",fill=dec)
qplot(x=dec,y=fun,data=n1, facets = ~gender,xlab="decision",ylab="fun",
      geom="boxplot",fill=dec)
#female has no preference on ambitious given 4 minute. 
qplot(x=dec,y=amb,data=n1, facets = ~gender,xlab="decision",ylab="ambitious",
      geom="boxplot",fill=dec)
#male prefer on sharing value compared to female
qplot(x=dec,y=shar,data=n1, facets = ~gender,xlab="decision",ylab="sharing value",
      geom="boxplot",fill=dec)
#male prefer young partners? 
qplot(x=dec,y=age_o,data=n1, facets = ~gender,xlab="decision",ylab="age of partner",
      geom="boxplot",fill=dec)
qplot(x=dec,y=prob,data=n1, facets = ~gender,xlab="decision",ylab="yes probability of partner",
      geom="boxplot",fill=dec)
qplot(x=dec,y=like,data=n1, facets = ~gender,xlab="decision",ylab="how much do you like",
      geom="boxplot",fill=dec)


#Check interaction term

# it seems that there are interaction terms between intelligent and sharing values
qplot(x = intel, y = shar, facets = ~gender, data = n1) +
  geom_smooth(method = "lm")
# it seems that there are interaction terms between ambitious and sharing values
qplot(x = amb, y = shar, facets = ~gender, data = n1) +
  geom_smooth(method = "lm")

qplot(x = fun, y = shar, facets = ~gender, data = n1) +
  geom_smooth(method = "lm")

qplot(x = sinc, y = shar, facets = ~gender, data = n1) +
  geom_smooth(method = "lm")
qplot(x = prob, y = like, facets = ~gender, data = n1) +
  geom_smooth(method = "lm")
qplot(x = attr, y = shar, facets = ~gender, data = n1) +
  geom_smooth(method = "lm")

#no difference for samerace in male or female
table(n1_m[,c("dec","samerace")])/sum(table(n1_m[,c("dec","samerace")]))
table(n1_f[,c("dec","samerace")])/sum(table(n1_f[,c("dec","samerace")]))



```

```{r}
# seeing difference betwen dec and attr divided by wave
# Choose group = 1, 3, 4, 6, 9, 10, 11, 13,  16, 17

set.seed(1000)
group <- sample(1:21,10, replace= F)
group

n1_m_sample = n1_m %>% filter(wave %in% group)
head(n1_m_sample)
ggplot(n1_m_sample,aes(x=dec, y=attr)) +
  geom_point(alpha = .5,colour="blue4") +
  geom_smooth(method="lm",col="red3") +
  labs(title="dec vs attr") +
  facet_wrap(~wave,ncol=4)

n1_f_sample = n1_f %>% filter(wave %in% group)
head(n1_f_sample)
ggplot(n1_f_sample,aes(x=dec, y=attr)) +
  geom_point(alpha = .5,colour="blue4") +
  geom_smooth(method="lm",col="red3") +
  labs(title="dec vs attr") +
  facet_wrap(~wave,ncol=4)



```


```{r}
#Check raondom intercept and slope 
nullmodel1 <- glmer( dec ~ 1 + (1|wave), data = n1, family=binomial(link="logit"))
nullmodel2 <- glmer( dec ~ 1 + (attr|wave), data = n1, family=binomial(link="logit"))
anova (nullmodel1, nullmodel2)
```



```{r}


##1. For male
# put everything together (AIC : 3153 , bic : 3239)
dec_n1 <- glmer(dec~attr+sinc+intel+fun+amb+shar + samerace + age_o + prob+like + (attr|wave), family=binomial(link="logit"), data = n1_m)
summary(dec_n1)


#dec_n3 <- glmer(dec~attr_c+age_o +sinc_c+intel_c+fun_c+amb_c+shar_c + samerace + (attr|wave), family=binomial(link="logit"), data = train_m)
#summary(dec_n3)

# adding interaction term  (AIC: 3134 BIC : 3220)
dec_m <- glmer(dec~attr_c+sinc_c+fun_c+amb_c+intel_c*shar_c  +samerace + prob_c+like_c + (attr|wave), family=binomial(link="logit"), data = n1_m)
summary(dec_m)

#coef(dec_m)

#ln interpretation 

anova (dec_n1, dec_m)

dotplot(ranef(dec_m, condVar=TRUE)) 

##2. For female

# put everything together (AIC : 3166 , bic : 3258)
dec_n1_f <- glmer(dec~ attr_c+sinc_c+fun_c+amb_c+intel_c*shar_c  +samerace + age_o+ prob_c+like_c+(attr|wave), family=binomial(link="logit"), data = n1_f)
summary(dec_n1_f)

# wihtout samerace and age (AIC: 3162 BIC : 3242)
dec_f <- glmer(dec~ attr_c+sinc_c+fun_c+amb_c+intel_c*shar_c+ prob_c+like_c+(attr|wave), family=binomial(link="logit"), data = n1_f)
summary(dec_f)


```


```{r}
## 1. For male
#confusion matrix

Conf_mat <- confusionMatrix(as.factor(ifelse(fitted(dec_m) >= 0.5, "1","0")),
                            as.factor(n1_m$dec),positive = "1")
Conf_mat$table
# accuracy: 0.8
Conf_mat$overall["Accuracy"];
Conf_mat$byClass[c("Sensitivity","Specificity")] 

#Roc curve
roc(n1_m$dec,fitted(dec_m),plot=T,print.thres="best",legacy.axes=T,
    print.auc =T,col="red3")


##2. For female
Conf_mat2 <- confusionMatrix(as.factor(ifelse(fitted(dec_f) >= 0.5, "1","0")),
                            as.factor(n1_f$dec),positive = "1")
Conf_mat2$table
#accuracy : 0.78
Conf_mat2$overall["Accuracy"];
Conf_mat2$byClass[c("Sensitivity","Specificity")] 

#Roc curve
roc(n1_f$dec,fitted(dec_f),plot=T,print.thres="best",legacy.axes=T,
    print.auc =T,col="red3")
```

```{r}
## 1. For male

rawresid <- residuals(dec_m,"resp")
#binned residual plots
binnedplot(x=fitted(dec_m),y=rawresid,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")

binnedplot(n1_m$attr_c,y=rawresid,xlab="Attractive centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_m$sinc_c,y=rawresid,xlab="Sinceree centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_m$intel_c,y=rawresid,xlab="Inteligent centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_m$fun_c,y=rawresid,xlab="Fun centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_m$amb_c,y=rawresid,xlab="Ambitious centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_m$shar_c,y=rawresid,xlab="Sharing Values centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_m$prob_c,y=rawresid,xlab="Prob centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_m$like_c,y=rawresid,xlab="Like centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")

##2. For female
rawresid2 <- residuals(dec_f,"resp")
#binned residual plots
binnedplot(x=fitted(dec_f),y=rawresid2,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")

binnedplot(n1_f$attr_c,y=rawresid2,xlab="Attractive centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_f$sinc_c,y=rawresid2,xlab="sincere centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_f$intel_c,y=rawresid2,xlab="intelligent centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_f$fun_c,y=rawresid2,xlab="Fun centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_f$amb_c,y=rawresid2,xlab="ambitious centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_f$shar_c,y=rawresid2,xlab="Sharing Value centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_f$prob_c,y=rawresid2,xlab="Prob centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
binnedplot(n1_f$like_c,y=rawresid2,xlab="Like centered",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
```



```{r}
# 2. Since the first method loses 20% of data, I try to impute every variable instead 

summary(dating3)
dating3_imp <- mice(dating3,m=1,defaultMethod=c("pmm","logreg","polyreg","polr"),print=F)
d2 <- mice::complete(dating3_imp)

stripplot(dating3_imp, col=c("grey","darkred"),pch=c(1,20))

#pmm looks better
densityplot(dating3_imp)

summary(d2)


```






```{r}
#PART1 EDA 

#female prefers to say yes when partner is attractive compared to male?
qplot(x=dec,y=attr,data=d2, facets = ~gender, xlab="decision",ylab="attractive",
      geom="boxplot",fill=dec)
qplot(x=dec,y=sinc,data=d2, facets = ~gender,xlab="decision",ylab="sincere",
      geom="boxplot",fill=dec)
qplot(x=dec,y=intel,data=d2, facets = ~gender,xlab="decision",ylab="intelligent",
      geom="boxplot",fill=dec)
qplot(x=dec,y=fun,data=d2, facets = ~gender,xlab="decision",ylab="fun",
      geom="boxplot",fill=dec)
#female has no preference on ambitious given 4 minute. 
qplot(x=dec,y=amb,data=d2, facets = ~gender,xlab="decision",ylab="ambitious",
      geom="boxplot",fill=dec)
#male prefer on sharing value compared to female
qplot(x=dec,y=shar,data=d2, facets = ~gender,xlab="decision",ylab="sharing value",
      geom="boxplot",fill=dec)
#male prefer young partners? 
qplot(x=dec,y=age_o,data=d2, facets = ~gender,xlab="decision",ylab="age of partner",
      geom="boxplot",fill=dec)
qplot(x=dec,y=prob,data=d2, facets = ~gender,xlab="decision",ylab="yes probability of partner",
      geom="boxplot",fill=dec)
qplot(x=dec,y=like,data=d2, facets = ~gender,xlab="decision",ylab="how much do you like",
      geom="boxplot",fill=dec)


#Check interaction term

# it seems that there are interaction terms between intelligent and sharing values
qplot(x = intel, y = shar, facets = ~gender, data = d2) +
  geom_smooth(method = "lm")
# it seems that there are interaction terms between ambitious and sharing values
qplot(x = amb, y = shar, facets = ~gender, data = d2) +
  geom_smooth(method = "lm")

qplot(x = fun, y = shar, facets = ~gender, data = d2) +
  geom_smooth(method = "lm")

qplot(x = sinc, y = shar, facets = ~gender, data = d2) +
  geom_smooth(method = "lm")
qplot(x = prob, y = like, facets = ~gender, data = d2) +
  geom_smooth(method = "lm")
qplot(x = attr, y = shar, facets = ~gender, data = d2) +
  geom_smooth(method = "lm")

```

```{r}
#Mean centering
d2$attr_c = d2$attr - mean(d2$attr)
d2$sinc_c = d2$sinc - mean(d2$sinc)
d2$intel_c = d2$intel - mean(d2$intel)
d2$fun_c = d2$fun - mean(d2$fun)
d2$amb_c = d2$amb - mean(d2$amb)
d2$shar_c = d2$shar - mean(d2$shar)
d2$prob_c = d2$prob - mean(d2$prob)
d2$like_c = d2$like - mean(d2$like)

# we analyze data by sex 
d2_m <- d2[d2$gender=='1',] 
d2_f <- d2[d2$gender=='0',] 


#no difference for samerace in male or female
table(d2_m[,c("dec","samerace")])/sum(table(d2_m[,c("dec","samerace")]))
table(d2_f[,c("dec","samerace")])/sum(table(d2_f[,c("dec","samerace")]))

```







```{r}
# For male 
# same model with above (AIC : 3533, bic : 3621)
dec2_m <- glmer(dec~attr_c+sinc_c+fun_c+amb_c+intel_c*shar_c  +samerace + prob_c+like_c + (attr|wave), family=binomial(link="logit"), data = d2_m)
summary(dec2_m)

#For female (AIC : 3722, BIC : 3803)

dec2_f <- glmer(dec~ attr_c+sinc_c+fun_c+amb_c+intel_c*shar_c+ prob_c+like_c+(attr|wave), family=binomial(link="logit"), data = d2_f)
summary(dec2_f)

```


```{r}
#third subset for matching (both way)
match1 <- subset(dating, select = c('iid','wave', 'pid','dec','match','gender','samerace','age_o','prob','like','attr3_1','sinc3_1','intel3_1','fun3_1','amb3_1','attr_o','sinc_o','intel_o','fun_o','amb_o','shar_o','prob_o','like_o'))


#only concerning the people who decide to meet the opposite partner
match1 <- match1 %>% filter(match1$dec==1)
summary(match1)
match1$pid[is.na(match1$pid)] <- 118
#remove NAs for values that are hard to estimate
match1 <- match1 %>% filter(!is.na(age_o))
match1 <- match1 %>% filter(!is.na(prob))
match1 <- match1 %>% filter(!is.na(like))
match1 <- match1 %>% filter(!is.na(attr3_1))
summary(match1)

match2 <- match1 %>% filter(!is.na(shar_o))
match2 <- match2 %>% filter(!is.na(amb_o))
match2 <- match2 %>% filter(!is.na(intel_o))
match2 <- match2 %>% filter(!is.na(sinc_o))
match2 <- match2 %>% filter(!is.na(prob_o))
match2 <- match2 %>% filter(!is.na(like_o))
summary(match2)

#change factor variable
str(match2)

match2$match <- factor(match2$match)
match2$gender <- factor(match2$gender)
match2$samerace <- factor(match2$samerace)

```

```{r}
# I tried norm rather than pmm because it estimates stably
match_imp <- mice(match2,m=1,defaultMethod=c("pmm","logreg","polyreg","polr"),print=F)
m1 <- mice::complete(match_imp)

stripplot(match_imp, col=c("grey","darkred"),pch=c(1,20))
stripplot(match_imp, attr~.imp|match, col=c("grey","darkred"),pch=c(1,20))

#pmm looks better
densityplot(match_imp)

summary(m1)


```

```{r}
#PART1 EDA 

qplot(x=match,y=age_o,data=m1, facets = ~gender, xlab="match",ylab="age of partner",
      geom="boxplot",fill=match)
qplot(x=match,y=prob,data=m1, facets = ~gender, xlab="match",ylab="probability to yes",
      geom="boxplot",fill=match)
qplot(x=match,y=prob_o,data=m1, facets = ~gender, xlab="match",ylab="partner's probability of yes",
      geom="boxplot",fill=match)
qplot(x=match,y=like,data=m1, facets = ~gender, xlab="match",ylab="like",
      geom="boxplot",fill=match)
qplot(x=match,y=like_o,data=m1, facets = ~gender, xlab="match",ylab="like of partner",
      geom="boxplot",fill=match)
qplot(x=match,y=attr3_1,data=m1, facets = ~gender, xlab="match",ylab="self attractive",
      geom="boxplot",fill=match)
qplot(x=match,y=sinc3_1,data=m1, facets = ~gender, xlab="match",ylab="self sincere",
      geom="boxplot",fill=match)
qplot(x=match,y=intel3_1,data=m1, facets = ~gender, xlab="match",ylab="self inteligent",
      geom="boxplot",fill=match)
# fun -> intersting 
qplot(x=match,y=fun3_1,data=m1, facets = ~gender, xlab="match",ylab="self fun",
      geom="boxplot",fill=match)
qplot(x=match,y=amb3_1,data=m1, facets = ~gender, xlab="match",ylab="self ambitious",
      geom="boxplot",fill=match)
qplot(x=match,y=attr_o,data=m1, facets = ~gender, xlab="match",ylab="partner's rating of attractive",
      geom="boxplot",fill=match)
qplot(x=match,y=sinc_o,data=m1, facets = ~gender, xlab="match",ylab="partner's rating of sincere",
      geom="boxplot",fill=match)
qplot(x=match,y=intel_o,data=m1, facets = ~gender, xlab="match",ylab="partner's rating of intel",
      geom="boxplot",fill=match)
qplot(x=match,y=fun_o,data=m1, facets = ~gender, xlab="match",ylab="partner's rating of fun",
      geom="boxplot",fill=match)
qplot(x=match,y=amb_o,data=m1, facets = ~gender, xlab="match",ylab="partner's rating of ambitious",
      geom="boxplot",fill=match)
qplot(x=match,y=shar_o,data=m1, facets = ~gender, xlab="match",ylab="partner's rating of share",
      geom="boxplot",fill=match)

#it does not make difference
table(m1[,c("match","samerace")])/sum(table(m1[,c("match","samerace")]))


#interaction term
qplot(x = fun_o, y = fun3_1, facets = ~gender, data = m1) +
  geom_smooth(method = "lm")
qplot(x = attr_o, y = attr3_1, facets = ~gender, data = m1) +
  geom_smooth(method = "lm")
#no difference on sincere
qplot(x = sinc_o, y = sinc3_1, facets = ~gender, data = m1) +
  geom_smooth(method = "lm")
qplot(x = intel_o, y = intel3_1, facets = ~gender, data = m1) +
  geom_smooth(method = "lm")
qplot(x = amb_o, y = fun3_1, facets = ~gender, data = m1) +
  geom_smooth(method = "lm")

basic_plot <- ggplot(m1,aes(x = fun_o, y = fun3_1, color = gender)) + theme_bw() 

# Colored scatterplot
basic_plot + geom_point(alpha = .3, size = .9) +geom_smooth(method = "lm")

```





```{r}
# we analyze data by sex 
m1_m <- m1[m1$gender=='1',] 
m1_f <- m1[m1$gender=='0',] 



##1. For male
#stepwise for male
NullModel = glm(match~1, data=m1_m, family=binomial)
FullModel = glm(match~ attr3_1*attr_o+sinc3_1*sinc_o+intel3_1*intel_o+fun3_1*fun_o+amb3_1*amb_o + samerace + age_o + prob* like+prob_o*like_o+shar_o*intel_o, data=m1_m, family=binomial)
stepwise_m=step(NullModel,scope=formula(FullModel),direction="both",trace=0)
summary(stepwise_m)

match_m <- glm(formula = match ~ like_o + attr_o + shar_o + prob + amb_o + fun_o + prob_o + sinc_o + intel_o + fun3_1 + like + shar_o:intel_o, family = binomial, data = m1_m)
summary(match_m)
exp(coef(match_m))


# put everything together (AIC : 1471)
match_m1 <- glm(match~attr3_1+sinc3_1+intel3_1+fun3_1+amb3_1 + samerace + age_o + prob* like+prob_o*like_o+attr_o+sinc_o+fun_o+amb_o+shar_o*intel_o, family=binomial(link="logit"), data = m1_m)
summary(match_m1)


##2. For female
#stepwise for female
NullModel1 = glm(match~1, data=m1_f, family=binomial)
FullModel1 = glm(match~ attr3_1+sinc3_1+intel3_1+fun3_1+amb3_1 + samerace + age_o + prob* like+prob_o*like_o+attr_o+sinc_o+fun_o+amb_o+shar_o*intel_o, data=m1_f, family=binomial)
stepwise_f=step(NullModel,scope=formula(FullModel),direction="both",trace=0)
summary(stepwise_f)

#best model (AIC: 1460)
match_f <- glm(match ~ like_o + attr_o + shar_o + prob + amb_o + fun_o + prob_o + sinc_o + intel_o + fun3_1 + like + shar_o:intel_o, family = binomial, data = m1_f)
summary(match_f)
exp(coef(match_f))


```
using stepwise BIC , 



```{r}
## 1. For male
#confusion matrix

Conf_mat <- confusionMatrix(as.factor(ifelse(fitted(match_m) >= 0.5, "1","0")),
                            as.factor(m1_m$match),positive = "1")
Conf_mat$table
# accuracy: 0.79
Conf_mat$overall["Accuracy"];
Conf_mat$byClass[c("Sensitivity","Specificity")] 

#Roc curve
roc(m1_m$match,fitted(match_m),plot=T,print.thres="best",legacy.axes=T,
    print.auc =T,col="red3")


##2. For female
Conf_mat2 <- confusionMatrix(as.factor(ifelse(fitted(match_f) >= 0.386, "1","0")),
                            as.factor(m1_f$match),positive = "1")
Conf_mat2$table
#accuracy : 0.79
Conf_mat2$overall["Accuracy"];
Conf_mat2$byClass[c("Sensitivity","Specificity")] 

#Roc curve
roc(m1_f$match,fitted(match_f),plot=T,print.thres="best",legacy.axes=T,
    print.auc =T,col="red3")
```

hierarchical logistic equation 
no issue with multicolinearity


how to interpret correlation in logistic results 

threshold? 
prediction ? 


Decision tree, random forest. ?






#Limitation




# Appendix 1 (Data)
```{r}


```
```


